---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# assignmentb1andb2haleymac

<!-- badges: start -->
<!-- badges: end -->

The goal of assignment-b1-and-b2-haleymac is to provide a function called histogram_maker() that creates histograms from specified data frame columns with a customizable bin width. 

## Installation

You can install the development version of assignment-b1-and-b2-haleymac like so:

``` r
install_github("stat545ubc-2022/assignment-b1-and-b2-haleymac", ref = "0.1.2")
```

Note to use the package in your current environment call it with no dashes, like so: 

``` r
library(assignmentb1andb2haleymac)
```

## Example

Here are two basic examples of how to use the histogram_maker function:
  Note that the histo_variable parameter should be in dataframe$columnname format

```{r example}
library(assignmentb1andb2haleymac)

histogram_maker(mtcars, mtcars$cyl, 1)

histogram_maker(mtcars, mtcars$mpg, 0.5)
```

